\chapter{Acknowledgement}
It all started with a bright summer's day in August when I timidly entered the simulation lab of the notorious department of Mathematical Modelling, Statistics and Bioinformatics. Now, ten months later, I can proudly present this master thesis. Despite the vast amount of work and the various complaints of my computer, I can confidently say that I consider this year as a very positive and enriching period of my student career. However, the result of this master dissertation would not have been the same without a few people and therefore I would like to pay them my respects. \\ \\
First of all, thank you Ingmar Nopens and Jan Baetens for your supervision and thorough corrections. Second of all, I would like to thank Wouter Naessens for being an awesome supervisor and providing guidance throughout this thesis. I am truly sorry for the hour-long, brain frying discussions on the force balance and the heavy workload I put on your shoulders during the first and last weeks. Michael Ghijs, for showing me the relativeness of deadlines and the relevance of the Beatles in data storage. May the lift force be with you! \\ \\
On a more serious note, thank you Timothy Van Daele for helping me with all my OpenFOAM, LaTeX and Github questions and good luck with the finalisation of your PhD. Stijn Van Hoey, for aiding me with the MATLAB, Github and Linux related questions. Next, a special notification for my fellow simulation lab thesis friends; Arthur, Laurentijn, Sofie, Annelies and Bavo for the occasional lighthearted chat and all members BIOMATH and KERMIT for the friendly and welcoming 
environment. Muchas gracias Jos\'e por los d\'atiles. \\ \\
On a more personal note, a special thanks to my girlfriend, Nancy, for the corrections, support and for being an amazing person. My parents, for all their unconditional support. Finally, I would like to thank \emph{``Wa boel \'e da ier?''} for all the great experiences during these five years at 't Boerekot and I wish you all the best of luck.

%giacomo